Too Beautiful to be Fake: Attractive Faces are Less Likely to be Judged as Artificially Generated

### 2024-10-08 submission/new_manuscript/manuscript.qmd
changes to manuscript and R1

---
title: "Too Beautiful to be Fake: Attractive Faces are Less Likely to be Judged as Artificially Generated"
# If blank, the running header is the title in upper case.
shorttitle: "Attractiveness and Reality"
# Set names and affiliations.
# It is nice to specify everyone's orcid, if possible.
# There can be only one corresponding author, but declaring one is optional.
author:
  - name: Dominique Makowski
    corresponding: true
    orcid: 0000-0001-5375-9967
    email: D.Makowski@sussex.ac.uk
    url: https://realitybending.github.io/
    roles:
      - Conceptualization
      - Data curation
      - Formal Analysis
      - Funding acquisition
      - Investigation
      - Methodology
      - Project administration
      - Resources
      - Software
      - Supervision
      - Validation
      - Visualization
      - Writing – original draft
    affiliations:
      - name: University of Sussex
        department: School of Psychology
  - name: An Shu Te
    #corresponding: 
    orcid: 0000-0002-9312-5552
    role:
      - Project administration
      - Resources
      - Writing – original draft
    affiliations:
      - name: Nanyang Technological University
        department: School of Social Sciences
  - name: Stephanie Kirk  # stephanie.morgank@gmail.com
    orcid: 0000-0002-9312-5552
    role:
      - Project administration
      - Resources
      - Writing – original draft
    affiliations:
      - name: Nanyang Technological University
        department: School of Social Sciences
  - name: Ngoi Zi Liang  # ziliang.ngoi@ntu.edu.sg
    #affiliation   : "2"
    role:
      - Project administration
      - Resources
      - Writing – review & editing
    affiliations:
      - name: Nanyang Technological University
        department: School of Social Sciences
  - name: Panagiotis Mavros  # panos.mavros@telecom-paris.fr
    #affiliation   : "3"
    orcid: 0000-0002-1540-5516
    role:
      - Supervision
      - Writing – review & editing
    affiliations:
      - name:  Télécom Paris
        department: Department of Economics and Social Sciences
  - name: S.H. Annabel Chen  # AnnabelChen@ntu.edu.sg
    role:
      - Project administration
      - Supervision
      - Writing – review & editing
    affiliations:
      - name: University of Sussex
        department: School of Psychology
      - name: Nanyang Technological University
        department: LKC Medicine
      - name: National Institute of Education
      - name: Nanyang Technological University
        department:  Centre for Research and Development in Learning

author-note:
  status-changes: 
    # Example: [Author name] is now at [affiliation].
    affiliation-change: ~
    # Example: [Author name] is deceased.
    deceased: ~
  # Disclosures condensed to one paragraph, but you can start a field with two line breaks to break them up: \n\nNew Paragraph
  disclosures:
    # Example: This study was registered at X (Identifier Y).
    study-registration: ~
    # Acknowledge and cite data/materials to be shared.
    data-sharing: ~
    # Example: This article is based on the dissertation completed by [citation].  
    related-report: ~
    # Example: [Author name] has been a paid consultant for Corporation X, which funded this study.
    conflict-of-interest: ~
    # Example: This study was supported by Grant [Grant Number] from [Funding Source].
    financial-support: ~
    # Example: The authors are grateful to [Person] for [Reason].
    gratitude: ~
    # Example. Because the authors are equal contributors, order of authorship was determined by a fair coin toss.
    authorship-agreements: ~
abstract: " Technological advances render the distinction between artificial (e.g., computer-generated faces) and real stimuli increasingly difficult, yet the factors driving our beliefs regarding the nature of ambiguous stimuli remain largely unknown. In this study, 150 participants rated 109 pictures of faces on 4 characteristics (attractiveness, beauty, trustworthiness, familiarity). The stimuli were then presented again with the new information that some of them were AI-generated, and participants had to rate each image according to whether they believed them to be real or fake. Despite all images being pictures of real faces from the same database, most participants did indeed rate a large portion of them as 'fake' (often with high confidence), with strong intra- and inter-individual variability. Our results suggest a gender-dependent role of attractiveness on reality judgements, with faces rated as more attractive being classified as more real. We also report links between reality beliefs tendencies and dispositional traits such as narcissism and paranoid ideation."
# Put as many keywords at you like, separated by commmas (e.g., [reliability, validity, generalizability])
keywords: [attractiveness, AI-generated images, fiction, fake news, sense of reality]
# If true, tables and figures are mingled with the text instead of listed at the end of the document.
floatsintext: true
# Numbered lines (.pdf and .docx only)
numbered-lines: true
# File with references
bibliography: references.bib
# Suppress title page
suppress-title-page: false
# Masks references that appear in the masked-citations list
mask: false
# Language options. See https://quarto.org/docs/authoring/language.html
lang: en
language:
  citation-last-author-separator: "and"
  citation-masked-author: "Masked Citation"
  citation-masked-date: "n.d."
  citation-masked-title: "Masked Title"
  title-block-author-note: "Author Note"
  title-block-correspondence-note: "Correspondence concerning this article should be addressed to"
  title-block-role-introduction: "Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows:"
  references-meta-analysis:
format:
  apaquarto-docx: default
  apaquarto-html: default
  apaquarto-pdf:
    # Can be jou (journal), man (manuscript), stu (student), or doc (document)
    documentmode: man
---

@@

Evidence suggests that inter-individual characteristics play a crucial role in simulation monitoring, with factors such as cognitive style, prior beliefs, and personality traits [@bryanov2021determinants; @ecker2022psychological; @sindermann2020short]. For instance, individuals with stronger analytical reasoning skills have been found to better discriminate real from fake stimuli [@pehlivanoglu2021role; @pennycook2019lazy], and prior knowledge or beliefs about the stimulus influences one's perception of it by biasing the attention deployment towards information that is in line with one's expectations [@britt2019reasoned]. Furthermore, dispositional traits, such as high levels of narcissism and low levels of openness and conscientiousness, have been associated with greater susceptibility to fake news [@piksa2022cognitive; @sindermann2020short].

@@

Beyond stimulus- and individual-related characteristics, evidence suggests that the interaction between the two (i.e., the subjective reaction associated with the experience of a given stimulus), contributes to simulation monitoring decisions. For instance, the intensity of experienced emotions have been shown to increase one's sense of presence - the extent to which one feels like "being there", as if the object of experience was real - when engaged in a fictional movie or a VR environment [@sanchez2005presence; @makowski2017being]. Indeed, participants' self-reported emotional arousal were found to significantly predict the probability that they would perceive images as real [@azevedo2020body]. Conversely, beliefs that emotional stimuli were fake (e.g., that emotional scenes were not authentic but instead involved actors and movie makeup) were found to result in emotion down-regulation [@makowski2019phenomenal; @sperduti2017distinctive]. In line with these findings, studies on susceptibility to fake news have also found heightened stimulus emotionality to be associated with greater belief [@martel2020reliance; @bago2022emotion], and higher neurophysiological arousal was predictive of judging realistic images as real [@azevedo2020body]. Additionally, other factors, such as the stimuli's perceived self-relevance [@sperduti2016paradox; @goldstein2009pleasure], as well as familiarity [@begg1992dissociation], could also play a role in guiding our appraisal of a stimulus.

<!-- Attractiveness -->

Due to their popularity as a target of CGI technology and the prospect offered with facial features that can be experimentally manipulated, AI-generated images of faces are increasingly used to study face processing [@dawel2021systematic], in particular in relationship with saliency or emotions, as well as to other important components of face evaluation, such as trustworthiness or attractiveness [@sobieraj2014beautiful; @balas2017; @tsikandilakis2019beauty; @calbi2017]. Interestingly, artificially created faces rated as more attractive (by an independent group of raters) were perceived as less real [@tucciarelli2020]. Conversely, @liefooghe2022faces reports that attractiveness ratings were significantly lower when participants who were told that the faces were AI-generated were compared to those who had no prior knowledge. Whereas this line of evidence suggests that reality beliefs have an effect on face attractiveness ratings, the opposite question - whether attractiveness contributes to the formation of reality beliefs - has received little attention to date.

@@

**Procedure.** 
In the first part of the study, participants answered a series of personality questionnaires presented in the order below. These include the *Mini-IPIP6*
<!-- (24 items) [@sibley2011]  -->
[24 items, @sibley2011]
measuring 6 personality traits, the *SIAS-6* and the *SPS-6*
<!-- (6 items each) [@peters2012development] -->
[6 items each, @peters2012development]
assessing social anxiety levels, 5 items we devised pertaining to expectations about AI-generated image technology ("I think current Artificial Intelligence algorithms can generate very realistic images"), of which we mixed with 5 items from the general attitudes towards AI scale to lower the former's saliency and the possibility of it priming the subjects about the task,
<!-- (*GAAIS*) [@schepman2020initial]. -->
[*GAAIS*, @schepman2020initial]
the *FFNI-BF*
<!-- (30 items) [@jauk2022validation] -->
[30 items, @jauk2022validation]
measuring 9 facets of narcissism; the *R-GPTS*
<!-- (18 items) [@freeman2021revised] -->
[18 items, @freeman2021revised]
measuring 2 dimensions related to paranoid thinking; and the *IUS-12*
<!-- (12 items) [@carleton2007fearing] -->
[12 items, @carleton2007fearing]
measuring intolerance to uncertainty. Self-rated attractiveness was also assessed using 2 items - one measuring general attractiveness
<!-- ("How attractive would you say you are?") [@marcinkowska2021self] -->
["How attractive would you say you are?", @marcinkowska2021self]
and the other measuring physical attractiveness
<!-- ("How would you rate your own physical attractiveness relative to the average") [@spielmann2020predictive] -->
["How would you rate your own physical attractiveness relative to the average", @spielmann2020predictive].
3 attention check questions were also embedded in the surveys.

In the second part of this study, 109 images of neutral-expression faces from the validated American Multiracial Face Database
<!-- (AMFD) [@chen2021broadening]  -->
[AMFD, @chen2021broadening]
were presented to the participants for 500ms each, in a randomized order, following a fixation cross display (750 ms). After each stimulus presentation, ratings of *Trustworthiness* ("I find this person trustworthy") and *Familiarity* ("This person reminds me of someone I know") were collected using visual analog scales. Notably, as facial attractiveness is a multidimensional construct, encompassing evolutionary, sociocultural, biological as well as cognitive aspects [@rhodes2006evolutionary; @han2018beauty], we assessed attractiveness using 2 visual analog scales, measuring general *Attractiveness* ("I find this person attractive") and physical *Beauty* ("This face is good-looking").

@@

We excluded 5 participants that either failed 2 (\>= 66.6%) or more attention check questions, took an implausibly short time to finish the questionnaires or had incomplete responses. The final sample included 145 participants (Mean age = 28.3, SD = 9.0, range: [19, 66]; Sex: 48.3% females, 51.0% males, 0.7% others).

**Data Analysis.**
The real-fake ratings (measured originally with a [-1, 1] analog scale) were converted into two scores, corresponding to two conceptually distinct mechanisms: the dichotomous *belief* (real or fake, based on the sign of the rating) and the *confidence* (the rating's absolute value) associated with that belief. The former was analyzed using logistic mixed models, which modelled the probability of assigning a face to the real (\>= 0) as opposed to fake (\< 0). The latter, as well as the other face ratings (attractiveness, beauty, trustworthiness and familiarity), was modelled using mixed beta regressions (suited for outcome variables expressed in percentages). The models included the participants and stimuli as random factors.

@@

<!-- Only one image file yielded a strong simulation monitoring bias (\> 85%), being classified as fake by 88.7% of participants. This image was removed from further analysis, leaving 108 trials per participant.  -->
On average, across participants, 44% of images (95%\~CI [0.12, 0.64]) were judged as fake and 56% of images (95%\~CI [0.36, 0.88]) as real. An intercept-only model with the participants and images as random factors showed that the Intraclass Correlation Coefficient (ICC), which can be interpreted as the proportion of variance explained by the random factors, was of 9.0% for the participants and 9.6% for the stimuli.

>>>>

---
title: "Too Beautiful to be Fake: Attractive Faces are Less Likely to be Judged as Artificially Generated"
shorttitle: "Attractiveness and Reality"
author:
  - name: Dominique Makowski
    corresponding: true
    orcid: 0000-0001-5375-9967
    email: D.Makowski@sussex.ac.uk
    url: https://realitybending.github.io/
    roles:
      - Conceptualization
      - Data curation
      - Formal Analysis
      - Funding acquisition
      - Investigation
      - Methodology
      - Project administration
      - Resources
      - Software
      - Supervision
      - Validation
      - Visualization
      - Writing – original draft
    affiliations:
      - name: University of Sussex
        department: School of Psychology
  - name: An Shu Te
    #corresponding: 
    orcid: 0000-0002-9312-5552
    role:
      - Project administration
      - Resources
      - Writing – original draft
    affiliations:
      - name: Nanyang Technological University
        department: School of Social Sciences
  - name: Stephanie Kirk  # stephanie.morgank@gmail.com
    orcid: 0000-0002-9312-5552
    role:
      - Project administration
      - Resources
      - Writing – original draft
    affiliations:
      - name: Nanyang Technological University
        department: School of Social Sciences
  - name: Ngoi Zi Liang  # ziliang.ngoi@ntu.edu.sg
    #affiliation   : "2"
    role:
      - Project administration
      - Resources
      - Writing – review & editing
    affiliations:
      - name: Nanyang Technological University
        department: School of Social Sciences
  - name: Panagiotis Mavros  # panos.mavros@telecom-paris.fr
    #affiliation   : "3"
    orcid: 0000-0002-1540-5516
    role:
      - Supervision
      - Writing – review & editing
    affiliations:
      - name:  Télécom Paris
        department: Department of Economics and Social Sciences
  - name: S.H. Annabel Chen  # AnnabelChen@ntu.edu.sg
    role:
      - Project administration
      - Supervision
      - Writing – review & editing
    affiliations:
      - name: University of Sussex
        department: School of Psychology
      - name: Nanyang Technological University
        department: LKC Medicine
      - name: National Institute of Education
      - name: Nanyang Technological University
        department:  Centre for Research and Development in Learning
author-note:
  status-changes: 
    # Example: [Author name] is now at [affiliation].
    affiliation-change: null
    # Example: [Author name] is deceased.
    deceased: null
  # Disclosures condensed to one paragraph, but you can start a field with two line breaks to break them up: \n\nNew Paragraph
  disclosures:
    # Acknowledge and cite data/materials to be shared.
    # Example. Because the authors are equal contributors, order of authorship was determined by a fair coin toss.
    # Example: This study was registered at X (Identifier Y).
    study-registration: null
    data-sharing: null
    # Example: This article is based on the dissertation completed by [citation].  
    related-report: null
    # Example: [Author name] has been a paid consultant for Corporation X, which funded this study.
    conflict-of-interest: null
    # Example: This study was supported by Grant [Grant Number] from [Funding Source].
    financial-support: null
    # Example: The authors are grateful to [Person] for [Reason].
    gratitude: null
    authorship-agreements: null
abstract: " Technological advances render the distinction between artificial (e.g., computer-generated faces) and real stimuli increasingly difficult, yet the factors driving our beliefs regarding the nature of ambiguous stimuli remain largely unknown. In this study, 150 participants rated 109 pictures of faces on 4 characteristics (attractiveness, beauty, trustworthiness, familiarity). The stimuli were then presented again with the new information that some of them were AI-generated, and participants had to rate each image according to whether they believed them to be real or fake. Despite all images being pictures of real faces from the same database, most participants did indeed rate a large portion of them as 'fake' (often with high confidence), with strong intra- and inter-individual variability. Our results suggest a gender-dependent role of attractiveness on reality judgements, with faces rated as more attractive being classified as more real. We also report links between reality beliefs tendencies and dispositional traits such as narcissism and paranoid ideation."
keywords: [attractiveness, AI-generated images, fiction, fake news, sense of reality]
floatsintext: true
numbered-lines: true
bibliography: references.bib
suppress-title-page: false
mask: false
# Language options. See https://quarto.org/docs/authoring/language.html
lang: en
language:
  citation-last-author-separator: "and"
  citation-masked-author: "Masked Citation"
  citation-masked-date: "n.d."
  citation-masked-title: "Masked Title"
  title-block-author-note: "Author Note"
  title-block-correspondence-note: "Correspondence concerning this article should be addressed to"
  title-block-role-introduction: "Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows:"
  references-meta-analysis:
format:
  apaquarto-docx: default
  apaquarto-html: default
  apaquarto-pdf:
    # Can be jou (journal), man (manuscript), stu (student), or doc (document)
    documentmode: man
editor: 
  markdown: 
    wrap: 72
---

@@

Evidence suggests that inter-individual characteristics play a crucial
role in simulation monitoring, with factors such as cognitive style,
prior beliefs, and personality traits [@bryanov2021determinants;
@ecker2022psychological; @sindermann2020short]. For instance,
individuals with stronger analytical reasoning skills have been found to
better discriminate real from fake stimuli [@pehlivanoglu2021role;
@pennycook2019lazy], and prior knowledge or beliefs about the stimulus
influences one's perception of it by biasing the attention deployment
towards information that is in line with one's expectations
[@britt2019reasoned]. Furthermore, dispositional traits, such as high
levels of narcissism and low levels of openness and conscientiousness,
have been associated with greater susceptibility to fake news
[@piksa2022cognitive; @sindermann2020short]. **Interestingly, a recent
review suggested that narcissism was related to a strong self-perceived
ability at detecting lies [@turi2022tangled], which could translate to
participants scoring high on narcissism providing more clear cut and
confidence responses. Conversely, those high in honesty-humility tend to
be more conservative in their judgments to ensure fairness
[@liu2020honesty], likely resulting in lower confidence ratings.**

@@

Beyond stimulus- and individual-related characteristics, evidence
suggests that the interaction between the two (i.e., the subjective
reaction associated with the experience of a given stimulus),
contributes to simulation monitoring decisions. For instance, the
intensity of experienced emotions have been shown to increase one's
sense of presence - the extent to which one feels like "being there", as
if the object of experience was real - when engaged in a fictional movie
or a VR environment [@sanchez2005presence; @makowski2017being]. Indeed,
participants' self-reported emotional arousal were found to
significantly predict the probability that they would perceive images as
real [@azevedo2020body]. Conversely, beliefs that emotional stimuli were
fake (e.g., that emotional scenes were not authentic but instead
involved actors and movie makeup) were found to result in emotion
down-regulation [@makowski2019phenomenal; @sperduti2017distinctive]. In
line with these findings, studies on susceptibility to fake news have
also found heightened stimulus emotionality to be associated with
greater belief [@martel2020reliance; @bago2022emotion], and higher
neurophysiological arousal was predictive of judging realistic images as
real [@azevedo2020body]. Additionally, other factors, such as the
stimuli's perceived self-relevance [@sperduti2016paradox;
@goldstein2009pleasure], as well as familiarity [@begg1992dissociation],
could also play a role in guiding our appraisal of a stimulus.**For
instance,** @miller2023 **reported that participants were more likely to
mistakenly identify AI-generated faces as real because they perceived
them as more familiar.**

<!-- Attractiveness and trustworthiness  -->

Due to their popularity as a target of CGI technology and the prospect
offered with facial features that can be experimentally manipulated,
AI-generated images of faces are increasingly used to study face
processing [@dawel2021systematic], in particular in relationship with
saliency or emotions, as well as to other important components of face
evaluation, such as trustworthiness or attractiveness
[@sobieraj2014beautiful; @balas2017; @tsikandilakis2019beauty;
@calbi2017]. Interestingly, artificially created faces rated as more
attractive (by an independent group of raters) were perceived as less
real [@tucciarelli2020]. Conversely, @liefooghe2022faces reports that
attractiveness ratings were significantly lower when participants who
were told that the faces were AI-generated were compared to those who
had no prior knowledge. **Similarly, when participants are informed that
faces are AI-generated, the perceived artificiality leads to lower trust
ratings [@wang2024], even when they are real faces
[@liefooghe2022faces]. In contrast, when participants are unaware that
the faces are AI-generated, trust ratings for these synthetic faces tend
to increase [@nightingale2022]**. Whereas this line of evidence suggests
that reality beliefs have an effect on face attractiveness and
**trustworthiness** ratings, the opposite question - whether
attractiveness **and trustworthiness contribute** to the formation of
reality beliefs - has received little attention to date.

@@

**Procedure.** In the first part of the study, participants answered a
series of personality questionnaires presented in the order below. These
include the *Mini-IPIP6* <!-- (24 items) [@sibley2011]  --> [24 items,
@sibley2011] measuring 6 personality traits, the *SIAS-6* and the
*SPS-6* <!-- (6 items each) [@peters2012development] --> [6 items each,
@peters2012development] assessing social anxiety levels, 5 items we
devised pertaining to expectations about AI-generated image technology
("I think current Artificial Intelligence algorithms can generate very
realistic images"), **to potentially test and mitigate the potential
effect of expectations/beliefs about AI.** **These items were** mixed
with 5 items from the general attitudes towards AI scale to lower the
former's saliency and the possibility of it priming the subjects about
the task, <!-- (*GAAIS*) [@schepman2020initial]. --> [*GAAIS*,
@schepman2020initial] the *FFNI-BF*
<!-- (30 items) [@jauk2022validation] --> [30 items,
@jauk2022validation] measuring 9 facets of narcissism; the *R-GPTS*
<!-- (18 items) [@freeman2021revised] --> [18 items,
@freeman2021revised] measuring 2 dimensions related to paranoid
thinking; and the *IUS-12* <!-- (12 items) [@carleton2007fearing] -->
[12 items, @carleton2007fearing] measuring intolerance to uncertainty.
Self-rated attractiveness was also assessed using 2 items - one
measuring general attractiveness
<!-- ("How attractive would you say you are?") [@marcinkowska2021self] -->
["How attractive would you say you are?", @marcinkowska2021self] and the
other measuring physical attractiveness
<!-- ("How would you rate your own physical attractiveness relative to the average") [@spielmann2020predictive] -->
["How would you rate your own physical attractiveness relative to the
average", @spielmann2020predictive]. 3 attention check questions were
also embedded in the surveys.

In the second part of this study, images of neutral-expression faces
from the validated American Multiracial Face Database
<!-- (AMFD) [@chen2021broadening]  --> [AMFD, @chen2021broadening] were
presented to the participants for 500ms each, in a randomized order,
following a fixation cross display (750 ms). T**he decision to present
the faces for 500 ms was based on pilot studies, which demonstrated that
this duration provides a sufficient perceptual window for
decision-making and aligns with previous research indicating stable
judgment levels and increased confidence beyond this exposure time
[@willis2006first].**

**The AMFD is a recently validated database including a set of 110
pictures of homogeneous quality featuring diverse faces (particularly in
terms of ethnicity), each (except one) posing with either a neutral or
smiling expression. We selected all 109 neutral images (89 women and 20
men) to reduce the influence of confounding factors like affect. The
AMFD primarily features racially ambiguous faces, representing multiple
racial categories such as multiracial, Latinx, and white. The database
includes 81 faces from individuals self-reporting two racial backgrounds
and 29 from those with three or more racial backgrounds: 33%
Asian/White, 22% Latinx/White, 11% Asian/Latinx, 6% White/Middle
Eastern, 5% Black/White, and 5% Asian/Middle Eastern, with about 18%
identifying as other racial backgrounds.**

After each stimulus presentation, ratings of *Trustworthiness* ("I find
this person trustworthy") and *Familiarity* ("This person reminds me of
someone I know") were collected using visual analog scales. Notably, as
facial attractiveness is a multidimensional construct, encompassing
evolutionary, sociocultural, biological as well as cognitive aspects
[@rhodes2006evolutionary; @han2018beauty], we assessed attractiveness
using 2 visual analog scales, measuring general *Attractiveness* ("I
find this person attractive") and physical *Beauty* ("This face is
good-looking"). **This dual-scale approach aims to reflect two
conceptually distinct dimensions: Attractiveness might capture personal,
Self-relevant and subjective appeal, whereas Beauty might be related to
a more “objective” decision based on aesthetic criteria that can be
recognized independently of personal attraction. In other words, we
wanted the experiment to be able to potentially capture scenarios where
a face could be judged beautiful yet not, attractive and vice versa.**

@@

We excluded 5 participants that either failed 2 (\>= 66.6%) or more
attention check questions, took an implausibly short time to finish the
questionnaires or had incomplete responses. The final sample included
145 participants (Mean age = 28.3, SD = 9.0, range: \[19, 66\]; Sex:
48.3% females, 51.0% males, 0.7% others).

**Data Analysis.** The real-fake ratings (measured originally with a
\[-1, 1\] analog scale) were converted into two scores, corresponding to
two conceptually distinct mechanisms: the dichotomous *belief* (real or
fake, based on the sign of the rating) and the *confidence* (the
rating's absolute value) associated with that belief. The former was
analyzed using logistic mixed models, which modelled the probability of
assigning a face to the real (\>= 0) as opposed to fake (\< 0). The
latter, as well as the other face ratings (attractiveness, beauty,
trustworthiness and familiarity), was modelled using mixed beta
regressions (suited for outcome variables expressed in percentages). The
models included the participants and stimuli as random factors.

@@

<!-- Only one image file yielded a strong simulation monitoring bias (\> 85%), being classified as fake by 88.7% of participants. This image was removed from further analysis, leaving 108 trials per participant.  -->

On average, across participants, 44% of images (95%\~CI \[0.12, 0.64\])
were judged as fake and 56% of images (95%\~CI \[0.36, 0.88\]) as real.
An intercept-only model with the participants and images as random
factors showed that the Intraclass Correlation Coefficient (ICC), which
can be interpreted as the proportion of variance explained by the random
factors, was of 9.0% for the participants and 9.6% for the stimuli.
